\documentclass[11pt,letterpaper]{article}

% Packages
\usepackage[margin=0.7in]{geometry}
\usepackage[table]{xcolor}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{tikz}
\usepackage{fancyhdr}
\usepackage{helvet} % Use Helvetica (Arial alternative) for pdfLaTeX
\usepackage{colortbl}
\usepackage{makecell}
\usepackage{paracol}

% Color definitions
\definecolor{darkblue}{RGB}{25,57,95}
\definecolor{mediumgray}{RGB}{128,128,128}
\definecolor{lightgray}{RGB}{240,240,240}

% Font settings for pdfLaTeX
\renewcommand{\familydefault}{\sfdefault} % Use sans-serif font

% Page setup
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

% Custom section formatting
\titleformat{\section}
{\color{darkblue}\large\bfseries}
{\thesection}{1em}{}
[\vspace{-8pt}\color{darkblue}\rule{\textwidth}{1pt}\vspace{2pt}]

\titleformat{\subsection}
{\color{darkblue}\normalsize\bfseries}
{\thesubsection}{1em}{}

% Custom commands
\newcommand{\metricbox}[3]{
    \begin{tikzpicture}
        \draw[fill=lightgray, draw=darkblue, thick] (0,0) rectangle (2.3,0.8);
        \node[anchor=west] at (0.1,0.55) {\textbf{\footnotesize #1}};
        \node[anchor=west] at (0.1,0.25) {\footnotesize #2: \textbf{#3}};
    \end{tikzpicture}
}

\newcommand{\riskitem}[2]{
    \textbf{\color{darkblue}#1:} #2
}

\begin{document}

% Header
\begin{center}
    {\Huge\color{darkblue}\textbf{Collaboration Partnership Analysis}}\\
    \vspace{4pt}
    {\large\color{mediumgray}Aetheris Navigation and Perception $\times$} {\large\color{mediumgray}SeeCORE}\\
    \vspace{2pt}
    {\footnotesize\color{mediumgray}05JUL25}
\end{center}

\section*{Executive Summary}
\vspace{-8pt}
\sloppy
\begin{multicols}{2}
\textbf{\color{darkblue}Key Takeaways:}
\begin{itemize}[leftmargin=10pt, itemsep=1pt]
    \item Further explore idea PoC collaboration between Aetheris and SeeCORE
    \item Fully communicate current Aetheris priorities and constraints
    \item Propose potential COAs for PoC from Aetheris side
\end{itemize}

\textbf{Strategic Value:} Based on our current understanding, this potential partnership offers significant market expansion opportunities across three high-value sectors neither company could independently address: oil \& gas inspection, industrial safety operations, and wide-area military perception, navigation, and operations. Operational synergies through integrated sensor intelligence and collaborative response platforms could enable revenue growth by combining physics-informed sensing with human-machine coordination across mission-critical applications.

\columnbreak

\textbf{Key Requirements to Advance Discussions:} Understanding of mutual capabiilties, alignment of priorities, timeline, PoC scope definition, and shared acknowledgement of mutual benefit.

\textbf{Timeline:} TBD - Aetheris currently on 9-12 month PoC execution timeline; SeeCORE currently desires 3-6 month PoC execution time frame.

\textbf{Capital Required:} TBD

\textbf{Risk Level:} Medium - manageable with proper mitigation strategies in place.

\textbf{Key Aetheris Constraints:} Limited development resources, capital requirements for execution, and technical development capacity constraints that impact project scope and delivery timelines.
\end{multicols}

\section*{Aetheris Capabilities}
Aetheris specializes in physics-informed neural networks (PINNs) that embed fundamental sensor physics directly into machine learning models. These models enable applications across sensor health monitoring, predictive maintenance, and real-time calibration systems for any sensor type. The primary complexity in deploying physics-informed models lies in generating the synthetic, partially synthetic, or field data necessary for validation and training. Aetheris initially focuses on optical systems due to their familiarity, relative usefulness, data accessibility, and development time advantages. 


For optical applications, data generation difficulty escalates from grayscale visible spectrum (fastest/cheapest) through color visible, NIR, LWIR, to MWIR imaging (most complex), directly impacting PoC development timelines and cost. This laborious data generation process enables substantially more robust models with fewer nodes, lower power consumption, faster execution speeds, and reduced training data requirements compared to conventional machine learning approaches. These physics-informed advantages create significant competitive differentiation in resource-constrained operational environments where model efficiency and reliability are critical.

Other capabilities that may prove useful in this PoC include sensor-fusion, 

\section*{Current Roadmap and Timeline}

\section*{PoC Development Strategy}
Aetheris employs a phased crawl-walk-run strategy for PoC development, targeting in-situ calibrations and optical system/sensor quality assurance and maintenance tracking capabilities. The PoC software will enable drone operators and maintainers to understand how data quality has evolved throughout the sensor's operational life and predict performance under specific mission parameters. For example, dashboard interfaces will provide operators with critical mission planning data such as maximum resolvable feature size at 500 ft altitude and identification of resolution "holes" in the sensor's performance spectrum.

\section*{Development Timeline Considerations}
While Aetheris operates as a B2B SaaS company in business model, our development timelines fall between traditional B2B SaaS and deep tech hardware companies due to the physics-intensive nature of our algorithms. Although we do not design or build hardware, we create software that understands the physics of hardware very intimately, requiring extensive validation and calibration processes. The magic of our algorithms lies in their attention to detail - precisely modeling the physical behaviors that determine sensor performance and degradation patterns.

\section*{Phased Implementation Approach}
\begin{itemize}[leftmargin=10pt, itemsep=1pt]
    \item \textbf{Crawl Phase:} Basic sensor health monitoring and physics parameter extraction
    \item \textbf{Walk Phase:} Predictive performance modeling and mission-specific capability assessment
    \item \textbf{Run Phase:} Full in-situ calibration and comprehensive quality assurance dashboard with real-time operational guidance
\end{itemize}


% Strategic Rationale

% \section*{Strategic Rationale}
% TBD
% \begin{paracol}{2}
% \textbf{\color{darkblue}Market Opportunity}
% \begin{itemize}[leftmargin=10pt, itemsep=1pt]
%     \item Access to new customer segments (industrial safety, oil \& gas inspection sectors previously inaccessible to either company independently)
%     \item Geographic expansion into US defense/industrial markets (Aetheris) and international military/industrial markets (SeeCORE)
%     \item Combined market presence creates unique positioning as integrated sensor intelligence + collaborative response platform
% \end{itemize}

% \textbf{\color{darkblue}Capability Enhancement}
% \begin{itemize}[leftmargin=10pt, itemsep=1pt]
%     \item Complementary technology platforms (physics-informed sensing + human-machine collaboration workflows)
%     \item Shared customer development and technical validation capabilities reduce market entry costs
%     \item Cross-domain expertise enables solutions neither company could develop independently \& boosts credibility
% \end{itemize}
% \switchcolumn

% \textbf{\color{darkblue}Competitive Positioning}
% \begin{itemize}[leftmargin=10pt, itemsep=1pt]
%     \item Creates barriers to entry through integrated platform complexity
%     \item Accelerates time-to-market by leveraging existing customer relationships and technical capabilities
%     \item Establishes potential market leadership in sensor-aware collaborative operational systems
% \end{itemize}

% \textbf{\color{darkblue}Strategic Alignment}
% \begin{itemize}[leftmargin=10pt, itemsep=1pt]
%     \item Aligns with both companies' expansion beyond core markets
%     \item Supports evolution toward platform-based business models
%     \item Enhances value proposition through comprehensive operational intelligence rather than point solutions
% \end{itemize}
% \end{paracol}

% Operational Framework
% \section*{Operational Framework}
% TBD
% % \begin{center}
% % \begin{tabular}{|l|l|l|}
% % \hline
% % \rowcolor{lightgray}
% % Function & Our Responsibilities & Partner Responsibilities \\
% % \hline
% % Sales \& Marketing & \makecell[l]{Lead generation, brand management} & \makecell[l]{Channel partnerships, regional sales} \\
% % \hline
% % Product Development & \makecell[l]{Core platform, technical architecture} & \makecell[l]{Specialized modules, integration} \\
% % \hline
% % Customer Support & \makecell[l]{Tier 1 support, documentation} & \makecell[l]{Tier 2/3 support, training} \\
% % \hline
% % Operations & \makecell[l]{Quality assurance, compliance} & \makecell[l]{Logistics, local operations} \\
% % \hline
% % \end{tabular}
% % \end{center}

% \vspace{6pt}
% \textbf{\color{darkblue}Governance Structure:} TBD

% % Financial Projections & Risk Mitigation (side by side)
% \begin{multicols}{2}
% \section*{Financial Projections}

% \textbf{\color{darkblue}Revenue Impact (3-Year)}
% \begin{center}
% \metricbox{Year 1}{\$}{[X]M}
% \metricbox{Year 2}{\$}{[X]M}
% \metricbox{Year 3}{\$}{[X]M}
% \end{center}

% \textbf{\color{darkblue}Key Metrics}
% \begin{itemize}[leftmargin=10pt, itemsep=1pt]
%     \item Customer acquisition cost: -[X]\%
%     \item Revenue per customer: +[X]\%
%     \item Market share: +[X] points
%     \item ROI: [X]\% by month 18
% \end{itemize}

% \textbf{\color{darkblue}Investment Breakdown}
% \begin{itemize}[leftmargin=10pt, itemsep=1pt]
%     \item Technology integration: \$[X]M
%     \item Marketing \& sales: \$[X]M
%     \item Personnel \& training: \$[X]M
%     \item Operations setup: \$[X]M
% \end{itemize}

% \columnbreak

% \section*{Risk Mitigation Plan}

% \riskitem{Market Risk}{Diversified go-to-market strategy across multiple segments and geographies.}

% \riskitem{Technical Risk}{Phased integration approach with fallback options and regular testing milestones.}

% \riskitem{Financial Risk}{Performance-based milestones with defined exit criteria and cost controls.}

% \riskitem{Operational Risk}{Clear SLAs, backup processes, and cross-training programs for critical functions.}

% \riskitem{Relationship Risk}{Formal governance structure, regular communication cadence, and conflict resolution processes.}

% \riskitem{Competitive Risk}{IP protection agreements, non-compete clauses, and market differentiation strategies.}

% \end{multicols}

% % Implementation Roadmap
% \section*{Implementation Roadmap}
% \begin{center}
% \begin{tabular}{|l|l|l|l|}
% \hline
% \rowcolor{lightgray}
% Phase & Key Deliverables & Success Criteria & Owner \\
% \hline
% 1: Foundation & \makecell[l]{Legal agreements,\\ team setup,\\ governance} & \makecell[l]{Contracts signed,\\ teams assembled} & Legal/HR \\
% \hline
% 2: Integration & \makecell[l]{Technical integration,\\ process alignment} & \makecell[l]{Systems connected,\\ processes defined} & IT/Ops \\
% \hline
% 3: Launch & \makecell[l]{Pilot programs,\\ initial customers} & \makecell[l]{First revenue,\\ customer feedback} & Sales/Marketing \\
% \hline
% 4: Scale & \makecell[l]{Full deployment,\\ performance optimization} & Target metrics achieved & All Teams \\
% \hline
% \end{tabular}
% \end{center}

% \vspace{8pt}

% % Footer
% \begin{center}
% \color{mediumgray}\footnotesize
% \textbf{Next Steps:} [Specific action items] | \textbf{Decision Required By:} [Date] | \textbf{Contact:} [Name, Email, Phone]
% \end{center}

\end{document}